Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-14 Paper_presentation.tex
Agora com tabelas corretamente numeradas
Contribuindo...

\documentclass[notes]{beamer}
\usepackage{graphicx}
\usepackage{url}
\usepackage[english, portuguese]{babel}
\usepackage[latin1, utf8]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\mode<presentation>

@@

@@

@@

\caption{Sizes of each GUID subgroup}

\begin{tabular}{ccc}\hline & \multicolumn{2}{c}{Network} \\

@@

\hline
\end{tabular}
\label{table2}

@@

\caption{Numbers of IP addresses per network sharing FOI}

\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Adresses} \\

@@

\end{tabular}
\label{table3}

>>>>

\documentclass[notes]{beamer}
\usepackage{graphicx}
\usepackage{url}
\usepackage[english, portuguese]{babel}
\usepackage[latin1, utf8]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\setbeamertemplate{caption}[numbered]
\mode<presentation>

@@

\addto\captionsportuguese{
\renewcommand{\figurename}{Figure}
\renewcommand{\tablename}{Table}
}

@@

\item[\checkmark] This study is based upon the analysis of a large number of observations of CP files on P2P networks.

\item[\checkmark] Also based upon the behavior of the peers that share these files.

\item[\checkmark] Most previous studies of P2P networks have taken place over just several days, or weeks, or a few months.

\item[\checkmark] This study is comprises of a thousand of observations per day for a full year.

\item[\checkmark] This duration is specially critical in criminal investigations.

\item[\checkmark] Scientific studies of crimes are often submitted as supporting facts during trial and sentencing.

\item[\checkmark] This study focus is on \textit{files of interest} (FOI).

\item[\checkmark] These files includes child pornography (CP) images, as well as stories, child erotica and collections associated with this kind of crimes.

\item[\checkmark] Only content with hashing values matching a list put together by law enforcement by visual inspection was logged.

\begin{frame}
\begin{block}{Background}

\item[\checkmark]This paper is based on data collected with the help of national and international law enforcement.

\item[\checkmark]Starting in January 2009, they began deploying a set of forensics tools for online investigations.

\item[\checkmark]Prior to these collaborative efforts, the standard method for online investigation of CP was to make isolated cases.

\item[\checkmark]Leads were not shared among agencies or offices, other than by phone or e-mail.

\item[\checkmark]Officers leverage their own experience to prioritize suspects.

@@

\begin{table}[H]
\centering

\caption{Sizes of each GUID subgroup} 
\label{tab:table2}
\begin{tabular}{ccc}\hline & \multicolumn{2}{c}{Network} \\

@@

\hline
\end{tabular}

@@

\caption{Numbers of IP addresses per network sharing FOI} 
\label{tab:table3}
\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Adresses} \\

@@

\end{tabular}
